Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2020-12-02 paper/results.tex
more typesetting improvements in fig. 6

\begin{figure}
	\centering
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model6_rasterized}{0.008585}{0.011885}{0.998152}{0.998152}{3.55}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model7_rasterized}{0.024634}{0.031499}{0.986202}{0.986198}{3.58}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model1_rasterized}{0.057670}{0.058917}{0.942217}{0.942178}{3.58}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model3_rasterized}{0.070818}{0.066410}{0.920779}{0.919694}{3.58}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model4_rasterized}{0.051033}{0.055558}{0.951106}{0.951073}{3.58}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model5_rasterized}{0.067856}{0.071096}{0.918668}{0.918393}{3.58}
	\end{minipage}

	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model2_rasterized}{0.067836}{0.074189}{0.913457}{0.913223}{3.58}
	\end{minipage}\hfill%
	\begin{minipage}{0.5\linewidth}
		\centering
		\surrogateplot{exp4_model8_rasterized}{0.061678}{0.091997}{0.894604}{0.894533}{3.58}
	\end{minipage}

	\caption{Regression performance of Models~1-8 (from left to right, top to
		bottom) trained in Experiment~4, viewed
		as true vs.~predicted TBR on a test set of a selected cross-validation
		fold. Points are coloured by density.}
	\label{fig:reg-performance}
\end{figure}

>>>>

	\hspace*{-0.06\linewidth}
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model6_rasterized}{0.008585}{0.011885}{0.998152}{0.998152}{3.79}
	\end{minipage}%
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model7_rasterized}{0.024634}{0.031499}{0.986202}{0.986198}{3.82}
	\end{minipage}

	\hspace*{-0.06\linewidth}
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model1_rasterized}{0.057670}{0.058917}{0.942217}{0.942178}{3.82}
	\end{minipage}%
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model3_rasterized}{0.070818}{0.066410}{0.920779}{0.919694}{3.82}
	\end{minipage}

	\hspace*{-0.06\linewidth}
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model4_rasterized}{0.051033}{0.055558}{0.951106}{0.951073}{3.82}
	\end{minipage}%
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model5_rasterized}{0.067856}{0.071096}{0.918668}{0.918393}{3.82}
	\end{minipage}

	\hspace*{-0.06\linewidth}
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model2_rasterized}{0.067836}{0.074189}{0.913457}{0.913223}{3.82}
	\end{minipage}%
	\begin{minipage}{0.53\linewidth}
		\centering
		\surrogateplot{exp4_model8_rasterized}{0.061678}{0.091997}{0.894604}{0.894533}{3.82}
	\end{minipage}

	\caption{Regression performance of Models~1-8 (from left to right, top to
		bottom) in Experiment~4, viewed
		as true vs.~predicted TBR on a test set of a selected cross-validation
		fold. Points are coloured by density.}
	\label{fig:reg-performance}
\end{figure}

### 2020-12-02 paper/ucl_tbr_paper.tex
increase size of fig. 3-5
more typesetting improvements in fig. 6

\newcommand{\surrogateplot}[6]{
\begin{tikzpicture}
	\node[anchor=south west,inner sep=0] at (0,0){\includegraphics[width=\textwidth]{#1}};
	\draw[black,fill=white,line
		width=0.05mm,align=right,font=\fontsize{5.5}{6.5}\selectfont]
		(0.42,#6) rectangle
		(2.45,2.5) node[pos=.5] {
			\\[0.1ex]
			$\mathrm{MAE} = \num{#2}$\\
			$S = \num{#3}$\\
			$R^2 = \num{#4}$\\
			$R^2_{\text{adj.}} = \num{#5}$
		};
	\draw[black,fill=white,line
		width=0.05mm,align=left,font=\fontsize{5.5}{7.5}\selectfont]
		(2.02,1.43) rectangle
		(4.05,0.38) node[pos=.5] {
			{\color{red}
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			\hskip1pt
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			} Ideal model\\
			{\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			\hskip1pt
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			} Trained model\\
			\hskip3pt\raisebox{0.25ex}{\scalebox{0.75}{\color{datacolor}\textbullet}}\hskip4pt Data
		};
\end{tikzpicture}}

>>>>

\newcommand{\surrogateplot}[6]{
\begin{tikzpicture}
	\node[anchor=south west,inner sep=0] at (0,0){\includegraphics[width=\textwidth]{#1}};
	\draw[black,fill=white,line
		width=0.05mm,align=right,font=\fontsize{5.5}{6.5}\selectfont]
		(0.42,#6) rectangle
		(2.55,2.7) node[pos=.5] {
			\\[0.1ex]
			$\mathrm{MAE} = \num{#2}$\\
			$S = \num{#3}$\\
			$R^2 = \num{#4}$\\
			$R^2_{\text{adj.}} = \num{#5}$
		};
	\draw[black,fill=white,line
		width=0.05mm,align=left,font=\fontsize{5.5}{7.5}\selectfont]
		(2.02,1.3) rectangle
		(4.3,0.38) node[pos=.5] {
			{\color{red}
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			\hskip1pt
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			} Ideal model\\
			{\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			\hskip1pt
			\leavevmode\leaders\hrule height 0.7ex
			depth\dimexpr0.4pt-0.7ex\hskip3pt\kern0pt
			} Trained model\\
			\hskip3pt\raisebox{0.25ex}{\scalebox{0.75}{\color{datacolor}\textbullet}}\hskip4pt Data
		};
\end{tikzpicture}}
